Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for Policy Response Under Climate Change

### 2020-08-19 Scripts/Manuscript.Rmd
Results draft

@@

Our results suggest that `r n_eez_per`% (n = `r n_eez`) of the world EEZs will see a change in SSR by early $21^{st}$ century (Fig. 1). The change in SSR will range from gains of over 100% of a sertain shared stock (e.g. Guatemala' SSR of *species* shared with Mexico is projected to go from 12% to 26%) to loses of up to -71% of SSR (e.g. Honduras SSR of *species* shared with the Nicaragua in the Pacific coast is projected to decline from 50% to 14%). Despite no substantial changes in SSR per EEZ can be seen by the mid $21^st$ century (**Supplements Fig 1 (map)**), changes in SSR are expected to increase in intensity (**Supplements Fig 2 (histogram)**).

@@

img <- readPNG("../Figures/figure_connections_n50.png")
grid.raster(img)

@@

![Average transboundary species SSR gain of neighbouring EEZs by 2030 (2021-2040) relative to 1951-2005 under RCP 8.5. Arrows go from the loosing EEZ (point) to the winner (arrowhead)](../Figures/figure_connections_n50.png)

## Time of Emergence Index
# Discussion

>>>>

max_values$per_early

@@

We estimate the changes from today (1951-2005) to the early (2020-2040) and mid $21^{st}$ century (2040-2060) in transboundary Stock Share Ratio between neighbouring countries. Our results suggest that `r n_eez_per`% (n = `r n_eez`) of the world EEZs will see a change in SSR by 2030 (Fig. 1A). While most EEZs will see and average species change lower than 20%, a few EEZs are expected to have 50% change in SSR (Fig. 2A). For example. Guatemala' SSR of *species* shared with Mexico is projected to go from 12% to 26% while Honduras SSR of *species* shared with the Nicaragua in the Pacific coast is projected to decline from 50% to 14%. Regions where EEZs are particularly small and/or have multiple borders (e.g. The Caribeean) will see a complex dynamic of changes in SSR (Fig. 2B). Towards the mid $21^st$ century, changes in SSR per EEZ will no be substantial (**Supplements Fig 1 (map)**) but are still are expected to increase in intensity (**Supplements Fig 2 (histogram)**).

@@

img <- readPNG("../Figures/Fig2.png")
grid.raster(img)

@@

![Average transboundary species SSR gain of neighbouring EEZs by 2030 (2021-2040) relative to 1951-2005 under RCP 8.5. Arrows go from the loosing EEZ (point) to the winner (arrowhead)](../Figures/Fig2.png)

## Time of Emergence

We estimated the time of emergence between neighbouring EEZs for 633 transbboundary stocks. On average, most of the world EEZ's time of emergence will be 2030 $\pm$ 25 yers (Fig S3-A), however, all EEZs have already seen changes for at least one species (Fig S3-B).

# Discussion
